\chapter{Section 4}
\section{Cognitive Walkthrough}
In order to make sure that our dashboard was suitable 
to the stakeholders mentioned in Section 2, we went 
through a cognitive walkthrough, which was divided in 
three charges: 
\begin{itemize}
    \item Outside the Group
    \begin{itemize}
    \item Analyser --> Someone from another project group 
    \end{itemize}
    \item Inside the Group
    \begin{itemize}
    \item Observer --> Writes down the analyser's performance
    \item Facilitator --> Explains the procedures to the 
    analyser
    \end{itemize}
\end{itemize} \par 
For the analyser part, we ended up with not one, but two 
analysers, whose names are the following:
\begin{itemize}
    \item Francisco Passos
    \item Vicente Torres
\end{itemize} \par
Each analyser was given two missions: "An alarming levels 
alert shows up. Verify." and "There is a fire taking place 
in Albergaria-a-Velha. Investigate.". Each mission was ranked 
from 0 to 2 (from "Bad" to "Great"), according to the 
analyser's performance. 
\subsection{Mission Description and Their Solutions}
    \begin{itemize}
        \item \textbf{Mission 1:} An alarming levels 
        alert shows up. Verify. \par 
        Solutions:
        \begin{itemize}
            \item Log Panel:
            \begin{itemize}
                \item Localize alert.
                \item Collect data for investigation.
            \end{itemize}
            \item Situation Panel: 
            \begin{itemize}
                \item Sensor changing.
                \item Verify the values. 
                \item Change to graphic panel.
            \end{itemize}
        \end{itemize}
        \item \textbf{Mission 2:} There is a fire taking place 
        in Albergaria-a-Velha. Investigate. \par 
        Solutions:
        \begin{itemize}
            \item Map:
            \begin{itemize}
                \item Select the fire gateway. 
            \end{itemize}
            \item Cameras Panel: 
            \begin{itemize}
                \item Observe the fire's scale.
            \end{itemize}
            \item Resources Panel: 
            \begin{itemize}
                \item Communicate with the means.
                \item Send more resources.
            \end{itemize}
        \end{itemize}
    \end{itemize}
\subsection{Results}
    \begin{table}[H]
        \centerline{%
            \begin{tabular}{lcc|cc}
                & \multicolumn{2}{c|}{Mission 1} & \multicolumn{2}{c}{Mission 2} \\ 
                \cline{2-3} \cline{4-5}
                & N. Errors & Results & N. Errors & Results \\ 
                \hline 
                Francisco Passos & 2 & 2 & 2 & 1 \\ 
                %\hline 
                Vicente Torres & 1 & 2 & 2 & 2 \\ 
                \hline 
                \textbf{Medium} & 1.5 & 2 & 2 & 1.5 
            \end{tabular}%
        }
    \caption{Results Table}
    \end{table}
\subsection{Detected Problems and Sketches in Low Fidelity}
\subsection{Conclusions}
    So, we come to the conclusion that 
\subsection{Changes}
\subsection{Sketches of Relevant Aspects in Graphical Interfaces}
\section{Heuristic Evaluation}
\section{Changes Made as a Result of the Evalutations}
\section{Overall Improvements Made}